07-logistic_regression

### 2019-02-21 journals/07-logistic_regression.Rmd
fit logistic model

```{r}
# Load libraries
library(lime)
```

@@

```{r}
# Fit a logistic regression model with only main effects
logit_main <- glm(samesource ~ ccf + rough_cor + D + sd_D + matches + mismatches + 
                    cms + non_cms + sum_peaks,
                  family = binomial(link = "logit"),
                  data = hamby173and252_train)

coef(logit_main)

logit_lime <- lime(x = hamby173and252_train %>% select(rf_features), 
                   model = logit_main)

logit_explain <- explain(x = hamby224_test %>% select(rf_features) %>% na.omit(), 
                         explainer = logit_lime, 
                         n_labels = 1,
                         n_features = 3)
```

>>>>

```{r}
# Load libraries
library(tidyverse)
library(lime)
```

@@

```{r}
# Fit a logistic regression model with only main effects
logit <- caret::train(as.factor(samesource) ~ ccf + rough_cor + D + sd_D + matches + 
                        mismatches + cms + non_cms + sum_peaks,
            data = hamby173and252_train, 
            method = "glm", 
            family = "binomial")

summary(logit)

logit_lime <- lime(x = hamby173and252_train %>% select(rf_features), 
                    model = logit)

logit_explain <- explain(x = hamby224_test %>% select(rf_features) %>% na.omit(), 
                          explainer = logit_lime, 
                          n_labels = 1,
                          n_features = 3)

plot_features(logit_explain[1:12,])
```
